Poster Data Analysis

### 2018-09-09 notebooks/poster_analysis.Rmd
minor updates

## Significance test for the percent presence of acquired genes between animal species
Only significant values will be presented in the table below (p < 0.05).
```{r message=FALSE, warning=FALSE}
acquired_genes_list <- resfinder_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, gene_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1)) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

>>>>

## Significance test for the percent presence of acquired genes between animal species
Only significant values will be presented in the table below (p < 0.05).
```{r message=FALSE, warning=FALSE}
acquired_genes_list <- resfinder_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, gene_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)
